### 2017-04-01 ThesisText/experiments.tex
Corrected typos

It is observable that for binary classes, Naive Bayes Classifiers performed
slightly better then decision trees. But for grade classes two by two and four
by four, decision trees were better. In particular, training models for binary
classes, understandably, yields better results on average.

@@

This dataset only contains features which have a number type. The records come
from the \texttt{Results} and \texttt{MoodleLogs} datasets.
Table~\ref{tab_dat_002} shows the features of this dataset.

@@

We observe from the results that Naive Bayes Classifiers perform better then
Decision Trees achieving greater levels of accuracy for each dataset variant.

>>>>

It is observable that for binary classes, Naive Bayes Classifiers performed
slightly better than decision trees. But for grade classes two by two and four
by four, decision trees were better. In particular, training models for binary
classes, understandably, yields better results on average.

@@

This dataset only contains features which have a number type. The records come
from the \texttt{Results} and \texttt{MoodleLogs} datasets.
Table~\ref{tab:dat_002} shows the features of this dataset.

@@

We observe from the results that Naive Bayes Classifiers perform better than
Decision Trees achieving greater levels of accuracy for each dataset variant.

### 2017-04-01 ThesisText/introduction.tex
Corrected typos

These E-Leaning platforms are called~\gls{lms}. The platforms
allow institutions not only to deliver training but also keep track of users,
courses, content, etc. In their normal operations, theses platforms generate
and store a lot of data. This data concerns the courses, the content in those
courses, activities from users, and so on. In some specific cases, like Moodle
in universities, the system may even keep track of the students grades.

@@

Before applying those techniques, we explore the original datasets of the
Moodle provided for this specific project. Section~\ref{sec:data} talks about
the original datasets, how they were explored, and how they were pre processed
into a data repository for use in this project.

Some statistical analysis are made to the pre processed data repository before
any~\gls{dm} techniques are applied. This is done in order to to understand the
contents of the data and know which~\gls{dm} techniques should be applied and
to which subset of the data repository those techniques should be applied to.
Section~\ref{sec:stats} talks about these statistics and draws some conclusions
from them.

>>>>

These E-Learning platforms are called~\gls{lms}. The platforms
allow institutions not only to deliver training but also keep track of users,
courses, content, etc. In their normal operations, theses platforms generate
and store a lot of data. This data concerns the courses, the content in those
courses, activities from users, and so on. In some specific cases, like Moodle
in universities, the system may even keep track of the students grades.

@@

Before applying those techniques, we explore the original datasets of the
Moodle provided for this specific project. Section~\ref{sec:data} talks about
the original datasets, how they were explored, and how they were preprocessed
into a data repository for use in this project.

Some statistical analysis are made to the preprocessed data repository before
any~\gls{dm} techniques are applied. This is done in order to to understand the
contents of the data and know which~\gls{dm} techniques should be applied and
to which subset of the data repository those techniques should be applied to.
Section~\ref{sec:stats} talks about these statistics and draws some conclusions
from them.

### 2017-04-01 ThesisText/sumario.tex
Corrected typos

E-Learning tem vindo a ganhar popularidade como forma de transmitir educação
devido aos avanços nas tecnologias, como a Internet. Instituições como
universidades e empresas têm vindo a a usar E-Learning para a transmissão de
educação para locais remotos estendendo o seu alcance a estudantes e
colaboradores que estão fisicamente distantes.

Sistemas chamado ``Learning Management Systemas'', como o Moodle, existem para
organizar E-Learning. Eles oferecem plataformas online onde professores e
educadores podem publicar conteúdo, organizar actividades, fazer avaliações, e
afins, de modo a que estudantes possam aprender e serem avaliados.

@@

Neste projecto, um repositório de dados do Moodle da Universidade de Évora é
explorado. Técnicas de aprendizagem supervisionada são aplicadas aos dados de
modo a mostrar como é possível prever o sucesso de estudantes a partir do seu
uso do Moodle. Métodos de aprendizagem não supervisionada são também aplicados
de modo a mostrar como há divisões nos dados.

>>>>

E-Learning tem vindo a ganhar popularidade como forma de transmissão de
conhecimentos a nível educacional graças aos avanços nas tecnologias, como por
exemplo, a Internet. Instituições como universidades e empresas têm vindo a
usar E-Learning para a transmissão de conteúdos educacionais para locais
remotos estendendo o seu alcance a estudantes e colaboradores que estão
fisicamente distantes.

Sistemas chamados ``Learning Management Systems'', como o Moodle, existem para
organizar E-Learning. Eles oferecem plataformas online onde professores e
educadores podem publicar conteúdo, organizar actividades, fazer avaliações, e
outro tipo de ações relacionadas, de modo a que os estudantes possam aprender e
serem avaliados.

@@

Neste projecto, um repositório de dados do Moodle da Universidade de Évora foi
explorado. Técnicas de aprendizagem supervisionada são aplicadas aos dados de
modo a mostrar como é possível prever o sucesso de estudantes a partir do seu
uso do Moodle. Métodos de aprendizagem não supervisionada são também aplicados
de modo a mostrar como há divisões nos dados.
